Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-09-06 Manuscript/manuscript.tex
Updated table list of simulations -- now shall contain almost all simulations with ECC-lipids The format of the table is yet to be discussed

\begin{table*}[tbp]
\centering
\caption{  List of MD simulations. 
           Given concentrations adopt the form $C_{bulk}/C_{buffer}$. 
        }
\todo{Joe: to be filled-in. I'll generate it automatically from my Jupyter notebooks.}  
\label{tbl:sim-list}
\begin{tabular}{l c c r r r r }
  lipid/counter-ions &  KCl (mM)  &  NaCl (mM) & CaCl$_2$\,(mM) &  \footnote{Number of lipid molecules with the largest mole fraction}N$_{\rm l}$   &  \footnote{Number of water molecules}N$_{\rm w}$ \todoi{Should confirm that the amounts of water in experiments matched those in simulations.}   &  \footnote{Simulation temperature}T (K)  \\
  \hline
    POPC:POPS (5:1)/K$^+$  & tba & tba & 60:12 & 9999 & 298  \\
    \hline
    POPC:POPS (5:1)/Na$^+$ & tba & tba & 60:12 & 9999 & 298  \\
    \hline
\end{tabular}
\end{table*}

>>>>

\begin{table*}[tbp]
\centering
\caption{  List of MD simulations. 
           %Given concentrations adopt the form $C_{bulk}/C_{buffer}$. 
        }
\label{tbl:sim-list}
\begin{tabular}{l c c r r r r r }
  lipid/counter-ions &  K  &  Na & Ca & Cl &  \footnote{Number of water molecules}N$_{\rm w}$ \todoi{Should confirm that the amounts of water in experiments matched those in simulations.}   &  \footnote{Number of lipid molecules with the largest mole fraction}N$_{\rm l}$     &  \footnote{Simulation temperature}T (K)  \\
  \hline
PC:PS (1:1)/CIon  &  0  &  64  &  0  &  0  &  5253  &  64:64  &  298 \\ 
PC:PS (1:1)/CIon  &  64  &  0  &  0  &  0  &  5253  &  64:64  &  298 \\ 
PC:PS (10:1)/CIon  &  0  &  6  &  0  &  0  &  3600  &  60:6  &  298 \\ 
PC:PS (10:1)/CIon  &  6  &  0  &  0  &  0  &  3600  &  60:6  &  298 \\ 
PC:PS (0:1)/CIon  &  72  &  0  &  0  &  0  &  3600  &  0:72  &  298 \\ 
PC:PS (0:1)/CIon  &  0  &  72  &  0  &  0  &  3600  &  0:72  &  298 \\ 
PC:PS (4:1)/CIon  &  0  &  12  &  0  &  0  &  3600  &  48:12  &  298 \\ 
PC:PS (4:1)/CIon  &  12  &  0  &  0  &  0  &  3600  &  48:12  &  298 \\ 
PC:PS (5:1)/CIon  &  0  &  12  &  13  &  26  &  3561  &  60:12  &  298 \\ 
PC:PS (5:1)/CIon  &  0  &  12  &  26  &  52  &  3522  &  60:12  &  298 \\ 
PC:PS (5:1)/CIon  &  0  &  12  &  0  &  0  &  3600  &  60:12  &  298 \\ 
PC:PS (5:1)/CIon  &  12  &  0  &  0  &  0  &  3600  &  60:12  &  298 \\ 
PC:PS (5:1)/CIon  &  0  &  12  &  39  &  78  &  3483  &  60:12  &  298 \\ 
PC:PS (5:1)/CIon  &  39  &  12  &  0  &  39  &  3483  &  60:12  &  298 \\ 
PC:PS (5:1)/CIon  &  0  &  51  &  0  &  39  &  3483  &  60:12  &  298 \\ 
  \hline
\end{tabular}
\end{table*}
